R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-03-05 README.Rmd
rename robspack to rtorf

```{r, eval = T}
tmp <- tempfile()
master <- df5
master$timeUTC <- as.character(master$timeUTC)
master$timeUTC_end <- as.character(master$timeUTC_end)
master$local_time <- as.character(master$local_time)

fwrite(master, 
       file =  "paper/tower_insitu_2020.txt",
       sep = " ")
```

@@

```{r, eval = T}
obs_write_csvy(dt = master,
          notes = "tower 2020",
          out = "paper/tower_insitu_2020.csvy")
```

@@

```{r, eval = F}
readLines("paper/tower_insitu_2020.csvy")[1:38]
```

@@

if(nrow(receptor_agl) > 0) {
  fwrite(x = receptor_agl,
         file = "paper/receptor_tower_insitu_2020_AGL.txt"),
  sep = " ")}

if(nrow(receptor_asl) > 0) {
  fwrite(x = receptor_asl,
         file = "paper/receptor_tower_insitu_2020_ASL.txt"),
  sep = " ")}

>>>>

```{r, eval = T}
master <- df5
master$timeUTC <- as.character(master$timeUTC)
master$timeUTC_end <- as.character(master$timeUTC_end)
master$local_time <- as.character(master$local_time)

fwrite(master, 
       file =  paste0(tempdir(), "/tower_insitu_2020.txt"),
       sep = " ")
```

@@

```{r, eval = T}
csvy <- paste0(tempdir(), "/tower_insitu_2020.csvy")
obs_write_csvy(dt = master,
               notes = "tower 2020",
               out = csvy
)
```

@@

```{r, eval = F}
readLines(csvy)[1:38]
```

@@

if(nrow(receptor_agl) > 0) {
  fwrite(x = receptor_agl,
         file = paste0(tempdir(), "/receptor_tower_insitu_2020_AGL.txt"),
         sep = " ")}

if(nrow(receptor_asl) > 0) {
  fwrite(x = receptor_asl,
         file = paste0(tempdir(), "/receptor_tower_insitu_2020_ASL.txt"),
         sep = " ")}
